---
title: "A3: SPL Library Checkouts"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
library("dplyr")
library("stringr")
library("tidyverse")
source("chart1_example.R")
source("summary.R")
source("chart2_example.R")
source("chart3.R")
```

### Introduction
With this dataset of prison and jail information from 1970 to 2018, I plan to observe the proportion of women in jail and in prison. I am planning to analyse the jail population of women (female_jail_pop) from more recent years, as the data is more accurate from 2015 on due to how the data is collected. For prison populations I will be analyzing female populations (female_prison_pop) but also female populations by race (aapi_female_prison_pop,black_female_prison_pop,latinx_female_prison_pop,native_female_prison_pop,other_race_female_prison_pop, and white_female_prison_pop). I will look at the proportion of females by race in the prison system by analyzing the female population variables and their race categories. I am hoping to develop some insight on female populations in prison, and how their race may affect the size of population.

An introduction of the data and a description of the trends/books/items you are choosing to analyze (and why!)

Using this dataset of all items checked out from the Seattle Public Library in 2022-2023, I plan to more specifically analyze Charles Dickens' books. I remember reading quite a few of his books as part of my high school's literature curriculum, so I was curious to see 

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

These will likely be calculated using your DPLYR skills, answering questions such as:

- What is the average number of checkouts for each item?
- What is the month or year with the most/least checkouts for a book that you're interested in?
- What is the month or year with the most/least checkouts for ebooks?
- How has the number of print book checkouts changed over time?

Feel free to calculate and report values that you find relevant.

### The Dataset

- Who collected/published the data?  
  - The Seattle Public Library provided this data as an open source dataset.
- What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?
  - The parameters of the data include: UsageClass, CheckoutType, MaterialType, CheckoutYear, CheckoutMonth, Checkouts, Title, ISBN, Creator, Subjects, Publisher, and PublicationYear.
- How was the data collected or generated?  
  - This data was collected on a monthly basis, counting the Seattle Public Library checkouts by title for physical and electronic items.
- Why was the data collected?  
  - This data was collected in order to record the different reading trends over time, such as how print and electronic items have changed or which authors/books became popular during certain periods of times. 
- What, if any, ethical questions do you need to consider when working with this data?  
- What are possible limitations or problems with this data?   (at least 200 words)

### First Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The first chart that you will create and include will show the trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title.
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

```{r Dickens_plot, echo = FALSE}
Dickens_plot

```

### Second Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The second chart that you will create and include will show another trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title.
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

```{r material_plot, echo = FALSE}
material_plot

```

### Your Choice

The last chart is up to you. It could be a line plot, scatter plot, histogram, bar plot, stacked bar plot, and more. Here are some requirements to help guide your design:

- You must have clear x and y axis labels
- The chart needs a clear title.
- You need a legend for your different line colors and a clear legend title

Here's an example of how to run an R script inside an RMarkdown file:

```{r bar_chart, echo = FALSE}
bar_chart

```


