---
title: "A3: SPL Library Checkouts"
author: "Emily Hao"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
library("dplyr")
library("stringr")
library("tidyverse")
source("chart1_example.R")
source("summary.R")
source("chart2_example.R")
source("chart3.R")
```

### Introduction

Using this dataset of all items checked out from the Seattle Public Library in 2022-2023, I plan to more specifically analyze Charles Dickens' books. I remember reading quite a few of his books as part of my high school's literature curriculum, so I was curious to see how popular his books were in relation to one another by analyzing how many of his books were checked out from the Seattle Public Library. I plan to compare data between physical and digital checkouts for his books, and by doing so, I hope to draw insight on current reading trends. I will also look at Charles' Dickens top books by total checkouts in order to see what his most popular and least popular books are, and how those trends changed or did not change between 2022 and 2023. 

### Summary Information

First, when filtering the entire 2022-23 dataset, I found that out of the `r total_spl_checkouts` total checkouts from the Seattle Public Library, `r total_dickens_checkouts` were of Charles Dickens' books. This makes the proportion of the total Charles' Dickens checkouts to the total amount of checkouts `r proportion`. 

In terms of comparing digital to physical book checkouts, there were `r digital_book_total_checkouts` total digital book checkouts and there were `r physical_book_total_checkouts` total physical book checkouts. Out of the digital book checkouts, the most checked out Charles Dickens book in one month is *`r digital_most_title_monthly`*, with `r digital_most_monthly_checkout` checkouts. The most checked out Charles Dickens physical book in one month is *`r physical_most_title_checkout`*, with `r physical_most_monthly_checkout` checkouts.

During the entire 2022 to 2023 time period, the Charles Dickens physical book with the most checkouts is *`r physical_title_most_checkouts`*, with `r physical_most_checkouts` checkouts. The Charles Dickens digital book with the most checkouts is *`r digital_title_most_checkouts`*, with `r digital_most_checkouts` checkouts.


### The Dataset

- Who collected/published the data?  
  - The Seattle Public Library provided this data as an open source dataset.
- What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?
  - The parameters of the data include: UsageClass, CheckoutType, MaterialType, CheckoutYear, CheckoutMonth, Checkouts, Title, ISBN, Creator, Subjects, Publisher, and PublicationYear.
- How was the data collected or generated?  
  - This data was collected on a monthly basis, counting the Seattle Public Library checkouts by title for physical and electronic items.
- Why was the data collected?  
  - This data was collected in order to record the checkouts of physical and digital library items. the different reading trends over time, such as how print and electronic items have changed or which authors/books became popular during certain periods of times. 
- What, if any, ethical questions do you need to consider when working with this data?  
- What are possible limitations or problems with this data?   (at least 200 words)

### First Trends Over Time Chart

```{r Dickens_plot, echo = FALSE}
Dickens_plot

```

### Second Trends Over Time Chart

```{r material_plot, echo = FALSE}
material_plot

```

### Your Choice

The last chart is up to you. It could be a line plot, scatter plot, histogram, bar plot, stacked bar plot, and more. Here are some requirements to help guide your design:

- You must have clear x and y axis labels
- The chart needs a clear title.
- You need a legend for your different line colors and a clear legend title

Here's an example of how to run an R script inside an RMarkdown file:

```{r bar_chart, echo = FALSE}
bar_chart

```


